---
title: "Interactivity"
output: html_document
date: "2025-10-23"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(readxl)
library(haven)
library(leaflet)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

```{r}
library(rvest)
library(tidyverse)
```

# My first function
```{r}
x_vec = rnorm(25, mean = 5, sd = 3)

(x_vec - mean(x_vec)) / sd(x_vec)
```

Write a function t compute z scores.
```{r}
z_scores = function(x) {
  
 z  = (x - mean(x)) / sd(x)
  
  z
}
```

Let's try out function ...
```{r}
z_scores(x=x_vec)

num_vec = rnorm(123, mean=14, sd=0.4)

z_scores(x=num_vec)
```

Let's break our function
```{r, error = TRUE}
z_scores(3)
z_scores("my name is jeff")
```

Write a new function t compute z scores.
```{r}
z_scores = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Z scores cannot be computed for length 1 vectors")
  }
  
  
 z  = (x - mean(x)) / sd(x)
  
  z
}
```


## Let's compute some stuff

Let's compute and return the mean and sd of a numeric vector.

```{r}
mean_and_sd = function(x) {
  
  
  if (!is.numeric(x)) {
    stop("The input x should be numeric")
  } 
  if (length(x) == 1) {
    stop("Only comput mean and sd when the input has 5 or more numbers")
  }
    
    mean_x = mean(x, na.rm = TRUE)
    sd_x = sd(x, na.rm = TRUE)
    
tibble(
  mean=mean_x,
  sd=sd_x
)

}

mean_and_sd(x_vec)
```


## Make up data..
Let's simulate some data

```{r}
sim_df = 
  tibble(
    x=rnorm(n=300, mean=5, sd=2)
  )

sim_df |>
  summarize(
    mu_hat = mean(x),
    sigma_hat = sd(x)
  )
```

Write a function to do simulations
```{r}
sim_mean_sd = function(n_subj= 30, mu = 3, sigma = 2) {
  
  sim_df = 
    tibble(
      x = rnorm(n=n_subj, mean = mu, sd = sigma)
    )
  
  sim_df |>
    summarize(
      mu_hat = mean(x),
      sigma_hat = sd(x)
    )
}
```

```{r}
sim_mean_sd(mu=48.4)
```


Import the LoTR data

```{r}
fellowship_ring = 
  read_excel("data/LotR_Words.xlsx", range = "B3:D6") |>
  mutate(movie = "Fellowship of the Ring")

two_towers = 
  read_excel("data/LotR_Words.xlsx", range = "F3:H6") |>
  mutate(movie = "Two Towers")

return_of_the_king = 
  read_excel("data/LotR_Words.xlsx", range = "J3:L6") |>
  mutate(movie = "Return of the King")

lotr_df =
  bind_rows(fellowship_ring, two_towers, return_of_the_king)
```


# Try to make a function instead
```{r}
lotr_import = function(cell_range, movie_title) {
  df = 
    read_excel("data/LotR_Words.xlsx", range = cell_range) |>
    mutate(movie=movie_title)
  
  df
}

fellowship = lotr_import(cell_range = "B3:D6", movie_title = "Fellowship")
two_towers = lotr_import(cell_range = "F3:H6", movie_title = "Two Towers")
return = lotr_import(cell_range = "J3:L6", movie_title ="Return")

bind_rows(fellowship, two_towers, return)
```


Write an import function
```{r}
nsduh_url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"

nsduh_html = read_html(nsduh_url)

data_marj = 
  nsduh_html |> 
  html_table() |> 
  nth(1) |>
  slice(-1) |> 
  select(-contains("P Value")) |>
  pivot_longer(
    -State,
    names_to = "age_year", 
    values_to = "percent") |>
  separate(age_year, into = c("age", "year"), sep = "\\(") |>
  mutate(
    year = str_replace(year, "\\)", ""),
    percent = str_replace(percent, "[a-c]$", ""),
    percent = as.numeric(percent)) |>
  filter(!(State %in% c("Total U.S.", "Northeast", "Midwest", "South", "West")))
```


```{r}
nsduh_table <- function(html, table_num, table_name) {
  
  table = 
    html |> 
    html_table() |> 
    nth(table_num) |>
    slice(-1) |> 
    select(-contains("P Value")) |>
    pivot_longer(
      -State,
      names_to = "age_year", 
      values_to = "percent") |>
    separate(age_year, into = c("age", "year"), sep = "\\(") |>
    mutate(
      year = str_replace(year, "\\)", ""),
      percent = str_replace(percent, "[a-c]$", ""),
      percent = as.numeric(percent),
      name = table_name) |>
    filter(!(State %in% c("Total U.S.", "Northeast", "Midwest", "South", "West")))
  
  table
  
}
```

